\blue{...Numerical investigation of viscous flow instabilities through heterogeneous porous media using adaptive and unstructured meshes under different mobility scenarios...}

### 2017-07-07 Papers/ViscousInstabilities/Manuscript_ViscousInstabilities_KC.tex
updates
do not rush kostas

\medskip
Flow instabilities may be due to pressure gradient along the interface of fluids, stress forces acting in opposite directions, mobility differences that may exceed critical limits and heterogeneities of the domain. \red{For example, during water flooding, efficiency is related with capillary number. The higher the capillary number the higher the recovery of hydrocarbons (LINK THESE SENTENCES ! HOW THIS NEW SENTENCE IS RELATED TO THE PREVIOUS -- 'Flow instabilities ... of the domain' ... AND HOW IS IT RELATED WITH THE FOLLOWING SENTENCES?)}. When the driving force of the injected fluid overcomes the capillary force, hydrodynamic instabilities may occur, resulting in the collapse of the interface between fluids and start forming fingers.

\medskip
Viscous instabilities (\ie fingering) can become more pronounced due to heterogeneities (\ie natural fractures, different permeability characteristics in different zones) of the porous medium therefore sweep efficiency may be reduced or early breakthrough may occur \citep{riaz_2004, tavassoli_2015}. During immiscible CO$_{2}$ flooding, density of supercritical CO$_{2}$ is usually lower than the \textit{in-situ} hydrocarbons, \red{therefore it may override oil (?)}. Viscosity of supercritical CO$_{2}$ is also significantly smaller than that of the oil thus viscous fingering and/or channelling may occur. The outcome of the above operations \textit{viscous fingering} \red{(Merge these 2 sentences ... remember sentences often need to be long than a single line and shorter than 3-4 lines!!)}.

>>>>

\medskip
Flow instabilities may be due to pressure gradient along the interface of fluids, stress forces acting in opposite directions, mobility differences that may exceed critical limits and heterogeneities of the domain. %\red{For example, during water flooding, efficiency is related with capillary number. The higher the capillary number the higher the recovery of hydrocarbons (LINK THESE SENTENCES ! HOW THIS NEW SENTENCE IS RELATED TO THE PREVIOUS -- 'Flow instabilities ... of the domain' ... AND HOW IS IT RELATED WITH THE FOLLOWING SENTENCES?)}. 
When the driving force of the injected fluid overcomes the capillary force, hydrodynamic instabilities may occur, resulting in the collapse of the interface between fluids and start forming fingers.

\medskip
Viscous instabilities (\ie fingering) can become more pronounced due to heterogeneities (\ie natural fractures, different permeability characteristics in different zones) of the porous medium therefore sweep efficiency may be reduced or early breakthrough may occur \citep{riaz_2004, tavassoli_2015}. During immiscible CO$_{2}$ flooding, density of supercritical CO$_{2}$ is usually lower than the \textit{in-situ} hydrocarbons, thus viscous fingering and/or channelling may occur.
